Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-11-01 latex/paper.tex
调整structure

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-10-29 21:07:47
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Chao-Yu Chen${}^{2}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

In this paper, we study the thermal conductivity of multilayer silicon structure by using the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}. Because of the abundant silicon structure model, the phase reconstruction has attracted much attention. In order to well simulate the structures of different phase by BTE, the latest Mod potential based on the large scale parallel and efficient LAMMPS molecular dynamics software package\cite{Parks2007} is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition. Firstly, we use conjugate gradient method to optimize these structures. All structures are shown in FIG.\ref{fig:structures}.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/structures}
  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicon. Within which (a) to (e) are top view and side view of bilayer structures. (f) to (g) are side view of trilayer structures and (h) is that of four-layers. The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface. All the atoms on the bottom surface are labeled as blue. The blacks represent those that are inside the structure. The top view of the cells is shown in the last.}
\end{figure}

For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc. ) and s indicates the type along the length direction with value of a (armchair) or z (zigzag). TABLE.\ref{tab:table1} lists the structure name, the minimum repeat cell periodicity, the binding energies, the first principle binding energies and the structural properties of the multilayer silicon. The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants. It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA). However, these first principle methods tend to overestimate the binding energy of materials and underestimate their equilibrium lattice constants. For this reason, the Mod potential is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.

From TABLE.\ref{tab:table1}, by comparing the binding energy of the first principles calculation of Guo is with that of MD, and from the point of view of stacking, the double layer of silicon is found more likely to form a monolayer of small and medium buckling slip stacking structure. The simulation is doing by velocity Verlet integral algorithm with the timestep to be $1 fs$. The length of the system in the x direction is $10 - 100nm$, the transverse direction y is in periodic boundary condition with its simulated width to be 5 nm, and free boundary condition is applied in z direction. At the same time the outermost two ends of the x direction are fixed, close to witch a 3nm with Nose-Hoover bath is applied. The left and right ends of the temperature control at $310K$ and $290K$. The simulation is carried out by NVT for $0.4ns$, then control the temperature gradient for $10 ns$, and finally we statistics the data of the last $10ns$. By Fourier's law, the relationship between thermal conductivity and heat flux is

\begin{equation}
  \kappa = \frac{ J_x}{ \nabla T \cdot S} \label{eq_nemd}
\end{equation}

where $\kappa$ stands for thermal conductivity, $J_x$ , $\nabla T=(T_L-T_R)/L_x$ is the average heat flux and temperature gradient along x direction respectively. $T_L$, $T_R$ and $L_x$ means the temperature of the two ends and the sample length between the heat baths. $S=W \cdot nd$ is the total cross area, where W,n,d is the size in the y direction, the layer number and the thickness of each layer. According to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.

@@

We firstly investigate the effect of surface reconstruction on thermal conductivity. 5 kinds of silicon structures of armchair and zigzag were selected to study. The relationship between the thermal conductivity and the length of bilayer silicon in different directions is shown in FIG.\ref{fig:tc_length_sheng}. the thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh. In addition, the structure with the thermal conductivity increasing significantly with the length is obviously anisotropy, different from single layer silicon and bulk silicon, who tend to be isotropic. In the aspect of structural, smooth 2l1 is most favorable for heat conduction, while 2l2 structure whose surface is made of a highly symmetrical and highly buckling pentacyclic ring "bird cage" is most unfavorable for thermal conductivity but suitable for thermoelectric materials. And the edges of the two directions are similar in shape, leading to small difference of heat transport.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for five types of bilayer silicon.b) The dependence on length of thermal conductivity for silicon with variable layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}. The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

@@

The thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table2}. It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure). In addition, the 2lr3 with small top and bottom buckling possesses the most anisotropy, which can reach 57.3\%. The smallest is 2l2 and 2lh (20\%). The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicon. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.

@@

The influence of thickness change on the thermal transport properties was then investigated. Here we study mainly on multilayer silicon structure with 3-10 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction. In order to compare, we also calculated the thermal conductivity of Si on its (111) surface and the thermal conductivity of the monolayer. The magnitude of the anisotropy is also shown in TABLE.\ref{tab:table2}. From the FIG.\ref{fig:vl_length}(a), in the case of the medium thickness of the 3 - 6 layers, the anisotropy of the multilayer silicon with zigzag type is higher than that of armchair. And with the increase of the number of layers, the anisotropy decreases gradually. The reason is that the zigzag direction of the multilayer silicon surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}). Compared with the bulk silicon structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow. While along the armchair direction, the fluctuation of multilayer silicon surface is very large, the same is its obvious affection on heat flow. This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicon. In order to predict the relationship between the thermal conductivity and the thickness, we calculated the thermal conductivity of the 8-10 layers silicene with the $2 \times 1$ surface reconstruction. In order to compare, the thermal conductivity of the bulk Si (111) surface with no surface reconstruction (9 layers) and the thermal conductivity of the monolayer were calculated. As shown in TABLE.\ref{tab:table2}, with the increase of thickness, the anisotropy decreases gradually. When the thickness is up to 10 layers, the anisotropy of the thermal transport of multilayer silicon can be neglected (only about 1.5\%), which is consistent with the results of bulk silicon and single silicon. On the other hand, as shown in FIG.\ref{fig:vl_length}(b), at the same thickness, in the case of shorter length (10 - 50nm), the anisotropy is obvious. When the length is about 100nm, the anisotropy difference becomes very small, and the size effect of the thermal conductivity anisotropy is obvious. This is essentially due to the difference in the out-of-plane acoustic branch (LA), the transverse acoustic branch (TA), and the vertical plane acoustic phonon (ZA) of the multilayer silicon structures along different directions. However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.

In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we calculated the phonon spectra of several typical structures. The $10 \times  10  \times  1$ multilayer structure is chosen. The selected high symmetry points are $\Gamma(0.0, 0.0, 0.0)$, $X(0.5, 0.0, 0.0)$,  $Y(0.0, 0.5, 0.0)$, Take points along $ X \rightarrow \Gamma \rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction. According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport. There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction. FIG.\ref{fig:bands}(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2. The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conducive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy. Accordingly, the three phonons in the two direction is almost the same as that in the 2l2, so the 2l2z and 2l2a are the least anisotropic structures with surface reconstruction. Comparing the two graphs, it can be found that all the group velocities of three phonons of 2l2 decrease. At the same time, the low frequency optical branch has the trend of moving down and couple with acoustic ones, which makes it less heat conducive, so that the 2l2 heat transport changes little with the length. The figure (c) (d) (e) is the dispersion of 3l1, 4l1, 6l1 $2 \times 1$ structure, all of whose three phonon group velocity are larger along zigzag than armchair. With the increase of layers, the optical branch participation gradually gathered in the high frequency area ($>15THz$), having almost no contribution to thermal conductivity while the vibration mode of the low frequency ($<5THz$) region is almost unchanged. On the other hand, with the increase of thickness, the acoustic velocity of armchair direction increases gradually, which prompts the decrease of anisotropic in multilayer silicon with the increase of layer number. Compared with phonon spectrum of the 6-layer structure(e), the difference between the 10 layers (f) is mainly the contribution of more atoms in the middle and high frequency ($>5THz$) region, which has little effect on the thermal conductivity.

Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime. The anisotropy could derive from these factors and it's worth finding the most important ones.

Heat capacity has large influence between the structures but has no contribution to anisotropy. We select all the phonons along  $\Gamma\rightarrow X$ , calculate each of their heat capacity with

\begin{equation}
  c_{k \sigma}=\frac{\hbar \omega_{k \sigma} }{V} \frac{\partial f(\omega_{k \sigma},T)}{\partial T}
\end{equation}

Where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function. The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$. The average heat capacity of the structures are shown in Table.\ref{tab:table2} . Large difference could be found between the $Cv$ of the structures. The lowest value is $10.15 kJ/m^3/K$ of 2lr while the highest value of Silicene could reach $606.4 kJ/m^3/K$, and this could lead to large difference between their thermal conductivity. There's no obvious trends when the layer increases but Silicene and 2l1 have pretty large value than the others and this has some relation to their low thickness.  Almost no difference could be found in the value along zigzag direction and armchair direction, even if $\omega_{k \sigma}$ has large deviation between the direction as shown in Fig.\ref{fig:bands}. This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high. That means when considering only acoustic phonons the heat capacity is close to constant.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/gv}{}
  \caption{\label{fig:gv} (color online)Group Velocity.}
\end{figure}

@@

The different localization situation  along each direction determines the anisotroy of group velocity  along that direction. To qualitatively measure the physical mechanism of phonon localization we carried out a vibrational eigenmode analysis. Mode localization can be quantitatively characterized by the phonon participation ratio $P_{k\sigma}$  \cite{Allen1999}for each eigen-mode $k\sigma$ as

\begin{equation}
  P_{k\sigma}= \frac{1}{N \sum_{i}
    {(\sum_\alpha{\epsilon^{i\alpha}_{k\sigma}
        \epsilon^{*i\alpha}_{k\sigma}})^2}}
\end{equation}

where N is the atom number and $\epsilon^{i\alpha}_{k\sigma}$ is the eigenvector component of mode $k\sigma$ for the i-th atom and $\alpha$ direction. The value of participation ratio is between 0 and 1 which measures the fraction of atoms participating a given phonon mode. If the mode is localized then its trends with N is O(1/N) while delocalized modes with O(1).

>>>>

% @Author: YangZhou
% @Date:   2017-06-20 20:27:38
% @Last Modified by:   YangZhou
% @Last Modified time: 2017-11-01 09:13:48
\documentclass[%
 reprint,
 amsmath,amssymb,
 aps,
 prb,
]{revtex4-1}
\preprint{APS/123-QED}
\usepackage{graphicx}% Include figure filesxx
\usepackage{bm}% bold math
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\begin{document}
\title{Anisotropic in-plane thermal conductivity observed in multilayer silicene}
\author{Yang Zhou${}^{1,3}$}
\author{Chao-Yu Chen${}^{2}$}
\author{Zhi-Xin Guo${}^{2}$}
\email{zxguo08@hotmail.com}
\author{Shi-You Chen${}^{1}$}
\author{Hong-Jun Xiang${}^{1}$}
\author{Xin-Gao Gong${}^{1,3}$}
\email{xggong@fudan.edu.cn}
\affiliation{
  ${}^1$Key Laboratory for Computational Physical Science (Ministry of Education), State Key Laboratory of Surface Physics and Department of Physics, Fudan University, Shanghai 200433, China\\
  ${}^2$Department of Physics, Xiangtan University, Xiangtan 411105, China\\
  ${}^3$Collaborative Innovation Center of Advanced Microstructures, Nanjing 210093, Jiangsu, China
}
\begin{abstract}
  By means of non-equilibrium molecular dynamics simulation, we systematically study the thermal transportation properties of different types of multilayer silicon. It is found that the thermal transport properties of multilayer silicon structures have significant surface effect and size effect in thickness direction. Surface reconstruction affects heat transport very well , the thermal conductivity of bilayer silicon with different reconstruction can reach up to $11.6 W/mK$, and can be as low as $1.2 W/mK$ and the anisotropy can be as high as $57.3\%$.With the increase of the number of layers, the thermal conductivity of the zigzag direction changed little, but the thermal conductivity increased significantly in the armchair direction, and the anisotropy of thermal conductivity decreased which is due to the smaller affection in more layer structure. This work could be helpful in the field of heat management, thermoelectric applications involving silicon and other multilayer nano materials in the future.
  \begin{description}
    \item[Keywords]
          Thermal conductivity, multilayer silicon, surface reconstruction, anisotropy
  \end{description}
\end{abstract}

@@

The thermal conductivity of multilayer silicon structures are studied with the Boltzmann transportation equation(BTE) method realized in ShengBTE\cite{Li2014}. In order to well simulate the structures of different phase by BTE, the latest Mod potential\cite{Parks2007} based on the large scale parallel and efficient LAMMPS molecular dynamics software package is chosen\cite{Kumagai2007Development}, which is able to reconstruct the silicon material elastic constants, the melting point and phase transition.The Mod potential is constructed for different type of silicon structures by fitting its bond angle parameter to give correct melting point and elastic constants. It refers to the elastic properties predicted with first principle local density approximation (LDA) and the generalized gradient approximation (GGA). However, these first principle methods tend to overestimate the binding energy of materials and underestimate their equilibrium lattice constants. For this reason, the Mod potential is constructed referring the correction of the equilibrium bond length based on the experimental diamond structure and leads to smaller the binding energy than that predicted by the first principle method.

All structures are shown in FIG.\ref{fig:structures}.For convenience, we define the names of these structures as "nlxs", where n is a pure number, representing the number of layers, l represents layer, x distinguishes different structures (concrete 1, 2, 3 etc. ) and s indicates the type along the length direction with value of a (armchair) or z (zigzag). TABLE.\ref{tab:table1} lists the structure name and  the minimum repeat cell periodicity of the multilayer silicon.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/structures}
  \caption{\label{fig:structures}  (color online) Some typical structure of multilayer silicon. Within which  are top view and side view of the studied structures. The buckling atoms on the top surface are labeled as yellow while the red atoms represent the others on the top surface. All the atoms on the bottom surface are labeled as blue. The greens represent those that are inside the structure. The orientation of top view of the cells is labeled as arrows.}
\end{figure}

Firstly, we use conjugate gradient method to optimize these structures.  According to the previous studies, we choose Si (111) layer spacing of $3.14 \angstrom$ as the thickness of each layer.

Where $c_{k \sigma}$ means heat capacity of phonon mode $k \sigma$, $v^{\alpha}$ present for mode group velocity and $\tau_{k \sigma}$ is phonon lifetime. The heat capacity  could be computed with Eq. \ref{eq:cv} .

\begin{equation}
  c_{k \sigma}=\frac{\hbar \omega_{k \sigma} }{V} \frac{\partial f(\omega_{k \sigma},T)}{\partial T} \label{eq:cv}
\end{equation}

Where $ f(\omega,T)=1/(exp(\frac{\hbar \omega}{k_b T})-1)$ is Bose-Einstein distribution function.

The calculations of $c_{k\sigma}$ , $v_{k\sigma,\alpha}$, and $\tau_{k\sigma}$ require second- and third-order force constants (FCs) as inputs. Both second- and third-order FCs are extracted from finite displacement method realized in Phonopy\cite{Togo2008} and Thridorder respectively. Both second-order and third-order  FCs are calculated with $3 \times 3 \times 1$ supercell with a $15\times 15 \times 3$ Monkhorst-Pack q-point mesh. The phonon group velocity  and transmision function are calculated with  with second order force constants. The interaction range of third-order FCs is truncated up to 4th neighbor. Iteration method is used instead of relaxation time approximision (RTA) to avoid underestimate of thermal concutivity.

@@

Surface reconstruction affects quite a lot on the intensity and anisotropy of thermal conductivity. The relationship between the thermal conductivity  and the length of three kinds of bilayer silicon along different directions is shown in FIG.\ref{fig:tc_length_sheng}(a). The thermal conductivity of 2l1 structure increases with the length the most significantly, followed by the 2l3 structure and 2lr3 structure, while the least significant is the structure of 2l2 and 2lh. In addition, the structure with the thermal conductivity increasing significantly with the length is obviously anisotropy, different from single layer silicon and bulk silicon, who tend to be isotropic. In the aspect of structural, smooth 2l1 is most favorable for heat conduction, while 2l2 structure whose surface is made of a highly symmetrical and highly buckling pentacyclic ring "bird cage" is most unfavorable for thermal conductivity but suitable for thermoelectric materials. And the edges of the two directions are similar in shape, leading to small difference of heat transport.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/tc_length_sheng}
  \caption{\label{fig:tc_length_sheng} (color online) a) The thermal conductivity dependence on length for three types of bilayer silicon.b) The dependence on length of thermal conductivity for silicon with variable layers.The scatters are the results of BTE calculations while the lines are fitted with Eq.\ref{eq_nemd}. The letter z/a in the legend mean the transport direction is zigzag/armchair.}
\end{figure}

@@

The thermal conductivity and anisotropy of multilayer silicon is shown in TABLE.\ref{tab:table1}. It can be seen from the table that the thermal conductivity of the bilayer silicon can reach up to 11.6 W/mK (2l1 structure). In addition, the 2lr3 with small top and bottom buckling possesses the most anisotropy, which can reach 57.3\%. The smallest is 2l2 and 2lh (20\%). The above results show that surface reconstruction has a significant effect on the thermal transport properties of multilayer silicon. The smooth surface is favorable for heat conduction, while the rough surface can greatly suppress the heat conduction. Meanwhile, the anisotropy of the surface structure leads to the significant anisotropy of the thermal conductivity.

@@

The influence of thickness change on the thermal transport properties was then investigated. Here we study mainly on multilayer silicon structure with 3-10 layers, whose  surface has typical Si (111) $2 \times 1$ surface reconstruction. In order to compare, we also calculated the thermal conductivity of Si on its (111) surface and the thermal conductivity of the monolayer. The magnitude of the anisotropy is also shown in TABLE.\ref{tab:table2}. From the FIG.\ref{fig:vl_length}(a), in the case of the medium thickness of the 3 - 6 layers, the anisotropy of the multilayer silicon with zigzag type is higher than that of armchair. And with the increase of the number of layers, the anisotropy decreases gradually. The reason is that the zigzag direction of the multilayer silicon surface is composed of a smooth zigzag atomic chain (as shown in FIG.\ref{fig:structures}). Compared with the bulk silicon structure, the heat conduction along the zigzag direction has no obvious effect on the heat flow. While along the armchair direction, the fluctuation of multilayer silicon surface is very large, the same is its obvious affection on heat flow. This difference is mainly caused by the surface reconstruction effect, and will decrease with the increase of the thickness of the silicon. In order to predict the relationship between the thermal conductivity and the thickness, we calculated the thermal conductivity of the 8-10 layers silicene with the $2 \times 1$ surface reconstruction. In order to compare, the thermal conductivity of the bulk Si (111) surface with no surface reconstruction (9 layers) and the thermal conductivity of the monolayer were calculated. As shown in TABLE.\ref{tab:table2}, with the increase of thickness, the anisotropy decreases gradually. When the thickness is up to 10 layers, the anisotropy of the thermal transport of multilayer silicon can be neglected (only about 1.5\%), which is consistent with the results of bulk silicon and single silicon. On the other hand, as shown in FIG.\ref{fig:vl_length}(b), at the same thickness, in the case of shorter length (10 - 50nm), the anisotropy is obvious. When the length is about 100nm, the anisotropy difference becomes very small, and the size effect of the thermal conductivity anisotropy is obvious. This is essentially due to the difference in the out-of-plane acoustic branch (LA), the transverse acoustic branch (TA), and the vertical plane acoustic phonon (ZA) of the multilayer silicon structures along different directions. However, with the increase of length, the ballistic transport is gradually saturated, and the difference of the heat transfer caused by the umklapp process is gradually reduced.
Heat capacity has large influence between the structures but has no contribution to anisotropy. We select all the phonons along  $\Gamma\rightarrow X$ ,
The values are averaged to get $Cv_z$ while those of phonons along $\Gamma\rightarrow Y$ are called $Cv_a$. The average heat capacity of the structures are shown in Table.\ref{tab:table1} . Large difference could be found between the $Cv$ of the structures. The lowest value is $10.15 kJ/m^3/K$ of 2lr while the highest value of Silicene could reach $606.4 kJ/m^3/K$, and this could lead to large difference between their thermal conductivity. There's no obvious trends when the layer increases but Silicene and 2l1 have pretty large value than the others and this has some relation to their low thickness.  Almost no difference could be found in the value along zigzag direction and armchair direction, even if $\omega_{k \sigma}$ has large deviation between the direction as shown in Fig.\ref{fig:bands}. This is due to the insensitivity of heat capacity to frequency when the frequency is low and the value is ignorable when frequency is relatively high. That means when considering only acoustic phonons the heat capacity is close to constant.

\begin{figure}[b]
  \includegraphics[width=0.48\textwidth]{images/gv}{}
  \caption{\label{fig:gv} (color online)Group Velocity versus phonon frequencies for both zigzag direction and armchair direction of the structures.The histogram bin width is chosen as 1.5THz.}
\end{figure}

@@

In order to understand the relationship between the thermal conductivity and the length of the different structures and different layers, we calculated the phonon spectra of several typical structures. The $10 \times  10  \times  1$ multilayer structure is chosen. The selected high symmetry points are $\Gamma(0.0, 0.0, 0.0)$, $X(0.5, 0.0, 0.0)$,  $Y(0.0, 0.5, 0.0)$, Take points along $ X \rightarrow \Gamma \rightarrow Y$ as shown in FIG.\ref{fig:bands}.According to the supercell structure, the zigzag boundary corresponds to $ \Gamma \rightarrow X$ direction in the dispersion, and the armchair boundary corresponds to $\Gamma\rightarrow Y$ direction. According to the relationship between the phonon spectrum and heat conduction, in the two-dimensional nano system, the acoustic phonon plays a major role in heat transport. There are a total of 3 acoustic branches, including the LA mode along the transmission direction, TA along the transverse and ZA mode along the perpendicular direction. FIG.\ref{fig:bands}(a) and (b) corresponds to the calculated spectra of the bilayer structure 2l1 and 2l2. The group velocity of $\Gamma\rightarrow X$ acoustic branch in 2l1 is obviously larger than that of $\Gamma\rightarrow Y$, making zigzag direction more heat conductive , which also verifies the difference between 2l1z and 2l1a thermal conductivity and anisotropy. Accordingly, the three phonons in the two direction is almost the same as that in the 2l2, so the 2l2z and 2l2a are the least anisotropic structures with surface reconstruction. Comparing the two graphs, it can be found that all the group velocities of three phonons of 2l2 decrease. At the same time, the low frequency optical branch has the trend of moving down and couple with acoustic ones, which makes it less heat conducive, so that the 2l2 heat transport changes little with the length. The figure (c) (d) (e) is the dispersion of 3l1, 4l1, 6l1 $2 \times 1$ structure, all of whose three phonon group velocity are larger along zigzag than armchair. With the increase of layers, the optical branch participation gradually gathered in the high frequency area ($>15THz$), having almost no contribution to thermal conductivity while the vibration mode of the low frequency ($<5THz$) region is almost unchanged. On the other hand, with the increase of thickness, the acoustic velocity of armchair direction increases gradually, which prompts the decrease of anisotropic in multilayer silicon with the increase of layer number. Compared with phonon spectrum of the 6-layer structure(e), the difference between the 10 layers (f) is mainly the contribution of more atoms in the middle and high frequency ($>5THz$) region, which has little effect on the thermal conductivity.
